Very simplified likelihood

### 2024-08-22 inst/very_simplified_likelihood.Rmd
further work on issue #240

```{r,label=likevis,cache=F}
plotter <- function(...){
a <- seq(from=0,to=1,by=0.01)
n <- 8
jj <- f_vec_arn(a,3,n,log=FALSE)
plot(a,jj/max(jj,na.rm=TRUE),type='n',xlab=expression(a),ylab="likelihood")
grid()
rain <- rainbow(n+1)
for(R in 1:n){
  y <- f_vec_a(a,R,n,log=FALSE)
  if(R==1){y[length(y)] <- 1}
  y <- y/max(y,na.rm=TRUE)
  if(R>1){y[length(y)] <- 0}
  points(a,y,type='l',lwd=4,col=rain[R])
}
abline(v=MLE(R=5,n=8))
text(0.07,0.95,"R=9",col=rain[9])
text(0.07,0.95,"R=8",col=rain[8])
text(0.20,0.95,"R=7",col=rain[7])
text(0.26,0.91,"R=6",col=rain[6])
text(0.29,0.83,"R=5",col=rain[5])
text(0.33,0.76,"R=4",col=rain[4])
text(0.35,0.64,"R=3",col=rain[3])
text(0.39,0.53,"R=2",col=rain[2])
text(0.45,0.41,"R=1",col=rain[1])
}

@@

```{r definelikeinsilico}
likeinsilico <- function(vec,M){
  alpha <- vec[1]
  beta  <- vec[2]
  S <- 0
  for(i in seq_len(nrow(M))){
    x <- M[i,1]
    LO <- alpha + beta * x
    p <- exp(LO)/(1+exp(LO))
    S <- S + f_vec_arn(p,M[i,2]-1,M[i,3]-1,log=TRUE)
  }
return(S)
}
```

@@

```{r calculate_parksupp,cache=TRUE}
S_parkrun <- function(a){f_vec_arn(a,r=results$place-1,results$runners-1,log=TRUE)}
(optparkrun <- optimize(S_parkrun, c(0.2,0.8),maximum=TRUE))

>>>>

```{r,label=likevis,cache=F}
plotter <- function(...){
a <- seq(from=0,to=1,by=0.01)
n <- 8
jj <- f_vec_arn(a,3,n,log=FALSE)
plot(a,jj/max(jj,na.rm=TRUE),type='n',xlab=expression(a),ylab="likelihood")
grid()
rain <- rainbow(n+1)
for(R in seq_len(n+1)){
  y <- f_vec_a(a,R,n,log=FALSE)
  if(R==1){y[length(y)] <- 1}
  y <- y/max(y,na.rm=TRUE)
  if(R>1){y[length(y)] <- 0}
  points(a,y,type='l',lwd=4,col=rain[R])
}
abline(v=MLE(R=5,n=8))
text(0.07,0.95,"R=9",col=rain[9])
text(0.20,0.95,"R=8",col=rain[8])
text(0.26,0.91,"R=7",col=rain[7])
text(0.29,0.83,"R=6",col=rain[6])
text(0.33,0.76,"R=5",col=rain[5])
text(0.35,0.64,"R=4",col=rain[4])
text(0.39,0.53,"R=3",col=rain[3])
text(0.45,0.41,"R=2",col=rain[2])
text(0.54,0.21,"R=1",col=rain[1])
}

@@

```{r definelikeinsilico}
likeinsilico <- function(vec,M){
  alpha <- vec[1]
  beta  <- vec[2]
  S <- 0
  for(i in seq_len(nrow(M))){
    x <- M[i,1]
    LO <- alpha + beta * x
    p <- exp(LO)/(1+exp(LO))
    S <- S + f_vec_arn(p,R=M[i,2],n=M[i,3]-1,log=TRUE)
  }
return(S)
}
```

@@

```{r calculate_parksupp,cache=TRUE}
S_parkrun <- function(a){f_vec_arn(a,R=results$place,results$runners-1,log=TRUE)}
(optparkrun <- optimize(S_parkrun, c(0.2,0.8),maximum=TRUE))
